\input{title.tex}

### 2023-07-29 docs/papers/04_response_letter/source/reviewer_2.tex
fix(project): :adhesive_bandage: response to reviewer #2

\subsection{\#2 Robustness}\label{sec:2-2}
% 导言:与流域和水资源相关的指标有很多，其中一些指标具有与治理和政策相关的参数。为了突出你所制定的IWGI的新颖性，也许你可以加上对其他相关指标的审查。
\RC{} I'm glad to see that you have included a couple of robustness checks. However, there are several more details related to Differenced Synthetic Control that need to be tested. These may include testing for the sensitivity of the results to changes in the choice of control group, the inclusion or exclusion of certain covariates, and the specification of the synthetic control model. Other possible robustness checks may involve testing for heterogeneity of treatment effects across different subgroups or time periods, and assessing the impact of outliers or influential observations on the results.

\AR{} Thanks for valuable suggestion. We now added a whole paragraph to the introduction:

\subsection{\#3 Results and discussion}\label{sec:2-3}
% 方程:方程(7)中的CEM是什么?还有，水的比例指的是什么?支持信息中公式(2)中的一些术语没有解释。例如:R或WU。
\RC{} The results, discussion, and comparisons are comprehensive, and I have no further comments at this time.

\AR{} We are glad that you found our results, discussion, and comparisons comprehensive. We appreciate your time and effort in reviewing our manuscript.

>>>>

\subsection{\#2 Robustness}\label{sec:2-2}

\RC{} I'm glad to see that you have included a couple of robustness checks. However, there are several more details related to Differenced Synthetic Control that need to be tested. These may include testing for the sensitivity of the results to changes in the choice of control group, the inclusion or exclusion of certain covariates, and the specification of the synthetic control model. Other possible robustness checks may involve testing for heterogeneity of treatment effects across different subgroups or time periods, and assessing the impact of outliers or influential observations on the results.

\AR{} We appreciate your thoughtful suggestion about additional robustness checks for our Differenced Synthetic Control (DSC) method. However, we have chosen not to include further robustness checks in our revised manuscript for several reasons:

\AR*{} Firstly, our primary objective in this paper is not to conduct a precisely quantitative assessment. Rather, we aim to uncover the interesting differential responses underlying the two different institutional shifts. As you pointed out, readers of our paper might not expect an overload of technical details. To maintain conciseness and avoid overwhelming our readers, we have chosen to limit the number of methodologies we include.

\AR*{} Secondly, the two approaches we have employed were recommended by the developers of the DSC method~\cite{engelbrektson2023}.
The corresponding algorithms have been provided and are consistent with the DSC method. If we were to introduce further tests, we might have to develop our own algorithms. This could potentially lead to inconsistencies and might confuse readers who wish to apply our methods in their own work.

\AR*{} Lastly, in response to a suggestion from another reviewer, we have revised the terminology from ``robustness'' to ``efficiency''. We believe this terminology better communicates our intentions and the nature of our methodology to readers, reducing the need for additional emphasis on robustness.

\AR*{} We believe these reasons justify our decision. However, we appreciate your suggestion and will certainly keep it in mind for future research where more extensive robustness checks may be more appropriate.

\subsection{\#3 Results and discussion}\label{sec:2-3}

\RC{} The results, discussion, and comparisons are comprehensive, and I have no further comments at this time.

\AR{} Thank you for your positive feedback on the comprehensiveness of the results, discussion, and comparisons in our paper. We're delighted to hear that you found this section satisfactory. Your kind words are greatly encouraging and motivate us to continue to improve our work. We hope that the revisions we have made in response to your helpful suggestions have improved the manuscript.
